---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# simanalyse

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.com/audrey-b/simanalyse.svg?branch=master)](https://travis-ci.com/audrey-b/simanalyse)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/audrey-b/simanalyse?branch=master&svg=true)](https://ci.appveyor.com/project/audrey-b/simanalyse)
[![Codecov test coverage](https://codecov.io/gh/audrey-b/simanalyse/branch/master/graph/badge.svg)](https://codecov.io/gh/audrey-b/simanalyse?branch=master)
[![License: GPL3](https://img.shields.io/badge/License-GPL3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.html)
[![Tinyverse status](https://tinyverse.netlify.com/badge/simanalyse)](https://CRAN.R-project.org/package=simanalyse)
[![CRAN status](https://www.r-pkg.org/badges/version/simanalyse)](https://cran.r-project.org/package=simanalyse)
![CRAN downloads](http://cranlogs.r-pkg.org/badges/simanalyse)
<!-- badges: end -->

simanalyse is an R package to analyse simulation study data and summarise results.

To install the latest development version from [GitHub](https://github.com/audrey-b/simanalyse)
```r
#install.packages("remotes")
remotes::install_github("audrey-b/simanalyse")
```

## Demonstration

### Simulate Data

Simulate 3 datasets using the sims package (we use only 3 datasets for demonstration purposes)
```{r}
library(simanalyse)
set.seed(10L)
params <- nlist(sigma = 2)
constants <- nlist(mu = 0)
code <- "for(i in 1:10){
          a[i] ~ dnorm(mu, 1/sigma^2)}"
sims <- sims::sims_simulate(code, 
                           parameters = params, 
                           constants = constants,
                           nsims = 3,
                           silent = TRUE)
print(sims)
```

### Analyse Data

Analyse all 3 datasets (here we use only a few iterations in debug mode for demonstration purposes; see ?sma_set_mode for details about analysis modes)
```{r}
prior <- "sigma ~ dunif(0, 6)"
results <- sma_analyse_bayesian(sims = sims,
                                code = code,
                                code.add = prior,
                                monitor = names(params),
                                mode = sma_set_mode("debug"))
```

### Derive new parameters (if required)

Derive posterior samples for new parameters. 
```{r}
results.derived <- sma_derive(results, "var=sigma^2", monitor="var")
print(results.derived)
```

The same transformation must be applied to the true parameter values for eventually evaluating the performance (e.g. bias) of the method for those new parameters, 

```{r}
params.derived <- sma_derive(params, "var=sigma^2", monitor="var")
print(params.derived)
```

### Summarise the results of the simulation study 

Evaluate the performance of the model using the 3 analyses
```{r}
sma_evaluate(results.derived, parameters=params.derived)
```
You may also create custom performance measures. The example below shows how to reproduce the results above with custom code.
```{r}
sma_evaluate(results.derived,
              measures = "", 
              parameters = params.derived, 
              custom_funs = list(estimator = mean,
                                 cp.low = function(x) quantile(x, 0.025),
                                 cp.upp = function(x) quantile(x, 0.975)),
              custom_expr_b = "bias = estimator - parameters
                              mse = (estimator - parameters)^2
                              cp.quantile = ifelse((parameters >= cp.low) & (parameters <= cp.upp), 1, 0)")
```

## Saving to file

When running simulation studies, it is often preferable to work from disk to keep a copy of all the results. You may save results to file by specifying the path using options(sims.path =), as follows:

```{r}
set.seed(10L)
options(sims.path = file.path(tempdir(), "sims"))

sims::sims_simulate(code, 
                    parameters = params, 
                    constants = constants,
                    nsims = 3,
                    exists = NA)

sma_analyse_bayesian(code = code,
                     code.add = prior,
                     monitor = names(params),
                     mode = sma_set_mode("debug"))

sma_derive(code="var=sigma^2", monitor="var")

sma_evaluate()
```

You may show the files created with
```{r}
files <- list.files(getOption("sims.path"), recursive=TRUE, all.files=TRUE)
print(files)
```

or read a particular file, e.g.
```{r}
readRDS(file.path(getOption("sims.path"), files[13]))
```

Here there is a discrepency with before because the seed argument as not been incorporated properly yet.

## Parallelization

Parallelization is achieved using the
[future](https://github.com/HenrikBengtsson/future) package.

To use all available cores on the local machine simply execute the
following code before calling `sims_analyse_bayesian()`, `sims_analyse_derive()` and/or `sims_analyse_evaluate()`.

    library(future)
    plan(multisession)

## Contribution

Please report any [issues](https://github.com/audrey-b/simanalyse/issues).

[Pull requests](https://github.com/audrey-b/simanalyse/pulls) are always welcome.

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/audrey-b/simanalyse/blob/master/CODE_OF_CONDUCT.md).
By contributing, you agree to abide by its terms.
