---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
```{r setup, include = FALSE}
dir.create(file.path(tempdir(), "sims"))
knitr::opts_knit$set(root.dir = file.path(tempdir(), "sims"))
```

# simanalyse

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R build status](https://github.com/audrey-b/simanalyse/workflows/R-CMD-check/badge.svg)](https://github.com/audrey-b/simanalyse/actions)
[![Codecov test coverage](https://github.com/audrey-b/simanalyse/workflows/test-coverage/badge.svg)](https://codecov.io/gh/audrey-b/simanalyse?branch=master)
[![License: GPL3](https://img.shields.io/badge/License-GPL3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.html)
[![CRAN status](https://www.r-pkg.org/badges/version/simanalyse)](https://cran.r-project.org/package=simanalyse)
![CRAN downloads](http://cranlogs.r-pkg.org/badges/simanalyse)
<!-- badges: end -->

simanalyse is an R package to facilitate model comparisons and simulation studies.

To install the latest development version from [GitHub](https://github.com/audrey-b/simanalyse)
```r
#install.packages("remotes")
remotes::install_github("audrey-b/simanalyse")
```

## Demonstration

### Simulate the Datasets

Simulate 100 datasets using the sims package.
```{r, results="hide", message=FALSE}
library(simanalyse)
set.seed(10L)
params <- list(sigma = 2)
constants <- list(mu = 0)
code <- "for(i in 1:10){
          y[i] ~ dnorm(mu, 1/sigma^2)}"
sims <- sims::sims_simulate(code, 
                            parameters = params, 
                            constants = constants,
                            nsims = 100,
                            silent = TRUE)
```

For example, the first dataset is
```{r}
sims[1]
```


### Analyse the Datasets

Conduct a Bayesian analysis of each dataset. Let's analyze each dataset in "report" mode. By default, this mode runs `r sma_set_mode("report")$n.chains` chains until the following two criteria are met: convergence based on r.hat <`r sma_set_mode("report")$r.hat` and a minimum effective sample size of `r sma_set_mode("report")$ess`. The first half of the chains is discarded as burnin. Chains are thinned to `r sma_set_mode("report")$n.save` iterations each to preserve disk and memory usage. See ?sma_set_mode for other choices of modes and customization.

```{r, results="hide", message=FALSE}
prior <- "sigma ~ dunif(0, 6)"
results <- sma_analyse(sims = sims,
                       code = code,
                       code.add = prior,
                       mode = sma_set_mode("report"))
```

For example, the posterior distribution obtained from the analysis of the first dataset is pictured below.
```{r}
plot(results[[1]])
```

### Derive New Parameters (if required)

Derive posterior samples for new parameters. 
```{r, results="hide", message=FALSE}
results.derived <- sma_derive(results, "var=sigma^2", monitor="var")
```
For example, the derived posterior distribution obtained for the first dataset is pictured below.
```{r}
plot(results.derived[[1]])
```
The same transformation must be applied to the true parameter values for eventually evaluating the performance (e.g. bias) of the method for those new parameters, 

```{r}
params.derived <- sma_derive(params, "var=sigma^2", monitor="var")
print(params.derived)
```

### Summarise the Results of the Simulation Study 

Evaluate the performance of the model using the 100 analyses:
```{r}
sma_evaluate(results.derived, parameters=params.derived)
```
Several more performance measures are available and can be specified using the *measures* argument (see ?sma_evaluate for details). You may also create custom performance measures. The example below shows how to reproduce the results above with custom code.
```{r}
sma_evaluate(results.derived,
             measures = "", 
             parameters = params.derived, 
             custom_funs = list(estimator = mean,
                                cp.low = function(x) quantile(x, 0.025),
                                cp.upp = function(x) quantile(x, 0.975)),
             custom_expr_b = "bias = estimator - parameters
                              mse = (estimator - parameters)^2
                              cpQuantile = ifelse((parameters >= cp.low) & (parameters <= cp.upp), 1, 0)")
```

## Saving to Files

When running lengthy simulation studies, it is often preferable to save all the results to disk. You may do this by using the functions ending in *files*. By default, results are saved in your working directory unless the *path* argument is specified.

```{r, results="hide", message=FALSE}
set.seed(10L)
sims::sims_simulate(code, 
                    parameters = params, 
                    constants = constants,
                    nsims = 100,
                    save = TRUE,
                    exists = NA)

sma_analyse_files(code = code,
                  code.add = prior,
                  mode = sma_set_mode("report"))

sma_derive_files(code="var=sigma^2", monitor="var")

sma_evaluate_files()
```

You may read specific files using the function *sma_read_files*. For example,

```{r}
sma_read_files(sma_evaluate_files)
```

Note that this result is identical to the result we obtained without saving to files,  using the same seed. The result is also identical when using parallelization, described below.

## Parallelization

Parallelization is achieved using the
[future](https://github.com/HenrikBengtsson/future) package.

To use all available cores on a local machine simply execute the following code before calling the package's functions.

```{r, eval=FALSE}
library(future)
plan(multisession)
```

Alternatively, if you wish to use a cluster computing environment (e.g. Compute Canada) with a workload manager (e.g. Slurm, Torque/PBS), simply execute the following code before calling the package's functions.

```{r, eval=FALSE}
library(future)
library(future.batchtools)
plan(batchtools_slurm, #for Slurm; see help(batchtools_template) for other options
     template = "batchtools.slurm.tmpl") #path to configuration file
```

For example, the following configuration file may be used with the Slurm manager:

```
#!/bin/sh

#SBATCH --time=00:10:00 ## walltime in hh:mm:ss
#SBATCH --ntasks=1 ## number of cores per dataset
#SBATCH --mem-per-cpu=1000 ## min memory per core in MB

## Export value of DEBUGME environment var to slave
export DEBUGME=<%= Sys.getenv("DEBUGME") %>
  
module load nixpkgs/16.09  gcc/7.3.0 r/4.0.2 ## load latest version of R
module load jags/4.3.0 ## load JAGS

Rscript -e 'batchtools::doJobCollection("<%= uri %>")'
```
The configuration file will be called for each dataset. Thus in this example, one new core (ntasks=1) will be requested for each dataset and the 100 datasets will be analyzed in parallel on a total of 100 cores.

## Contribution

Please report any [issues](https://github.com/audrey-b/simanalyse/issues).

[Pull requests](https://github.com/audrey-b/simanalyse/pulls) are always welcome.

## Code of Conduct

Please note that the simanalyse project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). 
By contributing to this project, you agree to abide by its terms.

