---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
```{r setup, include = FALSE}
dir.create(file.path(tempdir(), "sims"))
knitr::opts_knit$set(root.dir = file.path(tempdir(), "sims"))
```

# simanalyse

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R build status](https://github.com/audrey-b/simanalyse/workflows/R-CMD-check/badge.svg)](https://github.com/audrey-b/simanalyse/actions)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/simanalyse/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/simanalyse?branch=master)
[![License: GPL3](https://img.shields.io/badge/License-GPL3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.html)
[![CRAN status](https://www.r-pkg.org/badges/version/simanalyse)](https://cran.r-project.org/package=simanalyse)
![CRAN downloads](http://cranlogs.r-pkg.org/badges/simanalyse)
<!-- badges: end -->

simanalyse is an R package to facilitate model comparisons and simulation studies.

To install the latest development version from [GitHub](https://github.com/audrey-b/simanalyse)
```r
#install.packages("remotes")
remotes::install_github("audrey-b/simanalyse")
```

## Demonstration

### Simulate Data

Simulate 5 datasets using the sims package (here we use only a small number of datasets for the sake of illustration).
```{r}
library(simanalyse)
set.seed(10L)
params <- list(sigma = 2)
constants <- list(mu = 0)
code <- "for(i in 1:10){
          y[i] ~ dnorm(mu, 1/sigma^2)}"
sims <- sims::sims_simulate(code, 
                           parameters = params, 
                           constants = constants,
                           nsims = 5,
                           silent = TRUE)
print(sims)
```

### Analyse Data

Analyse the 5 datasets in "report" mode. This mode runs iterations until convergence, based on r.hat <`r sma_set_mode("report")$r.hat` and an effective sample size >`r sma_set_mode("report")$ess`. See ?sma_set_mode for other choices of analysis mode.
```{r}
prior <- "sigma ~ dunif(0, 6)"
results <- sma_analyse(sims = sims,
                                code = code,
                                code.add = prior,
                                mode = sma_set_mode("report", 
                                                    n.save=300, 
                                                    n.chains = 2))
```

### Derive new parameters (if required)

Derive posterior samples for new parameters. 
```{r}
results.derived <- sma_derive(results, "var=sigma^2", monitor="var")
print(results.derived)
```

The same transformation must be applied to the true parameter values for eventually evaluating the performance (e.g. bias) of the method for those new parameters, 

```{r}
params.derived <- sma_derive(params, "var=sigma^2", monitor="var")
print(params.derived)
```

### Summarise the results of the simulation study 

Evaluate the performance of the model using the 3 analyses
```{r}
sma_evaluate(results.derived, parameters=params.derived)
```
Several more performance measures are available and can be specified using the *measures* argument (see ?sma_evaluate for details). You may also create custom performance measures. The example below shows how to reproduce the results above with custom code.
```{r}
sma_evaluate(results.derived,
              measures = "", 
              parameters = params.derived, 
              custom_funs = list(estimator = mean,
                                 cp.low = function(x) quantile(x, 0.025),
                                 cp.upp = function(x) quantile(x, 0.975)),
              custom_expr_b = "bias = estimator - parameters
                              mse = (estimator - parameters)^2
                              cpQuantile = ifelse((parameters >= cp.low) & (parameters <= cp.upp), 1, 0)")
```

## Saving to file

When running simulation studies, it is often preferable to save all the results to disk. By default, when the *path* argument is not specified, results are saved in your working directory.

```{r}
set.seed(10L)
sims::sims_simulate(code, 
                    parameters = params, 
                    constants = constants,
                    nsims = 5,
                    save=TRUE,
                    exists = NA)

sma_analyse(code = code,
                     code.add = prior,
                     mode = sma_set_mode("report", 
                                         n.save=300, 
                                         n.chains = 2))

sma_derive(code="var=sigma^2", monitor="var")

sma_evaluate()
```

You may show the files created with
```{r}
files <- list.files(getwd(), recursive=TRUE, all.files=TRUE)
print(files)
```

and read a particular file, e.g.
```{r}
readRDS(file.path(getwd(), files[9]))
```


## Parallelization

Parallelization is achieved using the
[future](https://github.com/HenrikBengtsson/future) package.

To use all available cores on the local machine simply execute the following code before calling any of the package's functions.

    library(future)
    plan(multisession)

## Contribution

Please report any [issues](https://github.com/audrey-b/simanalyse/issues).

[Pull requests](https://github.com/audrey-b/simanalyse/pulls) are always welcome.

## Code of Conduct

Please note that the simanalyse project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). 
By contributing to this project, you agree to abide by its terms.

