---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# simanalyse

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.com/audrey-b/simanalyse.svg?branch=master)](https://travis-ci.com/audrey-b/simanalyse)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/audrey-b/simanalyse?branch=master&svg=true)](https://ci.appveyor.com/project/audrey-b/simanalyse)
[![Codecov test coverage](https://codecov.io/gh/audrey-b/simanalyse/branch/master/graph/badge.svg)](https://codecov.io/gh/audrey-b/simanalyse?branch=master)
[![License: GPL3](https://img.shields.io/badge/License-GPL3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.html)
[![Tinyverse status](https://tinyverse.netlify.com/badge/simanalyse)](https://CRAN.R-project.org/package=simanalyse)
[![CRAN status](https://www.r-pkg.org/badges/version/simanalyse)](https://cran.r-project.org/package=simanalyse)
![CRAN downloads](http://cranlogs.r-pkg.org/badges/simanalyse)
<!-- badges: end -->

simanalyse is an R package to analyse simulation study data and summarise results.

## Installation

To install the latest release version from [CRAN](https://cran.r-project.org)
```r
install.packages("simanalyse")
```

To install the latest development version from [GitHub](https://github.com/audrey-b/simanalyse)
```r
#install.packages("remotes")
remotes::install_github("audrey-b/simanalyse")
```

## Demonstration

Simulate 5 datasets using the sims package (we use only 5 datasets for demonstration purposes)
```{r}
library(simanalyse)
set.seed(10L)
params <- nlist(mu=0)
dat <- sims::sims_simulate("a ~ dnorm(mu,1)", parameters = params, nsims=5)
```

Analyse all 5 datasets (here we use only a few iterations for demonstration purposes)
```{r}
result <- simanalyse_analyse_bayesian(datalist=dat,
                                      code = "a ~ dnorm(mu,1)
                                              mu ~ dunif(-3,3)",
                                      n.adapt = 101,
                                      n.burnin = 0,
                                      n.iter = 101,
                                      monitor = "mu")
```

Summarize the results over the 5 datasets
```{r}
simanalyse_summarise(result, "bias", parameters=params)
```

## Contribution

Please report any [issues](https://github.com/audrey-b/simanalyse/issues).

[Pull requests](https://github.com/audrey-b/simanalyse/pulls) are always welcome.

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/audrey-b/simanalyse/blob/master/CODE_OF_CONDUCT.md).
By contributing, you agree to abide by its terms.
